---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CoxStream

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/coxstream)](https://CRAN.R-project.org/package=coxstream)
[![R-CMD-check](https://github.com/SignorinoY/coxstream/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/SignorinoY/coxstream/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/SignorinoY/coxstream/graph/badge.svg)](https://app.codecov.io/gh/SignorinoY/coxstream)
<!-- badges: end -->

The goal of coxstream is to ...

## Installation

You can install the development version of coxstream like so:

``` {r, eval = FALSE}
# install.packages("pak")
pak::pak("SignorinoY/coxstream")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(coxstream)
## basic example code
formula <- Surv(time, status) ~ X1 + X2 + X3 + X4 + X5
fit <- coxstream(
  formula, sim[sim$batch_id == 1, ],
  n_basis = 7, boundary = c(0, 3), idx_col = "patient_id", nu = 0.4
)
for (batch in 2:10) {
  fit <- update(fit, sim[sim$batch_id == batch, ])
}
summary(fit)
```
Besides the estimated coefficients, we can also obtain the estimated baseline hazard function. The following code plots the estimated cumulative baseline hazard function and the true cumulative baseline hazard function.
```{r evaluation, fig.alt = "Cumulative Baseline Hazard (Estimate vs True)"}
time <- seq(0, 3, length.out = 100)
basehaz_pred <- basehaz(fit, time)
basehaz_true <- cbind(time, 0.5 * time^2)
plot(
  time, basehaz_pred[, 2],
  type = "l", lty = 2,
  ylim = range(basehaz_pred[, 4], basehaz_pred[, 5]),
  xlab = expression(t), ylab = expression(Lambda[0](t)),
  main = "Cumulative Baseline Hazard (Estimate vs True)"
)
polygon(
  c(time, rev(time)), c(basehaz_pred[, 4], rev(basehaz_pred[, 5])),
  col = rgb(0.5, 0.5, 0.5, 0.4), border = NA
)
lines(basehaz_true[, 1], basehaz_true[, 2])
legend("topleft", legend = c("Estimate", "True"), lty = c(2, 1))
```
